### 2014-11-24 ms/ms.Rmd

In addition, we thank the following people for contributions to the following studies:
```{r,results="asis",echo=FALSE, message=FALSE}
getAcknowledgments <- function(studyName) {
  metadata  <-  readStudyFile(studyName, "studyMetadata.csv")
  i <- match("Acknowledgements",metadata$Topic)
  out <- ""
  if(!is.na(i))
    out <- sprintf(" **%s:** %s;", studyName, metadata$Description[i])
  out
}
writeLines(paste(sapply(unique(data$studyName), getAcknowledgments), collapse= ""))
```
.

>>>>

In addition, we thank the following people for contributions to the following studies:
```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(get_acknowledgements(baad))
```
.

### 2014-11-24 reports/report.Rmd

```{r, echo=FALSE}
source('report-fun.R')
```

# Report for study: `r .study`

@@

**Data contributor:** `r .dat$contacts$name`

**Email:** `r paste0(.dat$contacts$email[.dat$contacts$email!=""], collapse = ", ")`

@@

`r paste0("- ", .dat$contacts$address, collapse = "\n")`

@@

**Citation:** `r .dat$references$citation`

**DOI:** `r  paste0('[', bibGetElement(.dat$bibtex, element = "doi"), '](http://doi.org/', bibGetElement(.dat$bibtex, element = "doi"),')')`

**Abstract:** `r  bibGetElement(.dat$bibtex, element = "abstract")`

@@

The dataset includes records for `r length(.dat$data$studyName)` individuals from `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` family(ies), presenting `r length(unique(.dat$data$pft))` functional type(s), growing in `r length(unique(.dat$data$growingCondition))` condition(s) within `r length(unique(.dat$data$vegetation))` major type(s) of habitat, with data included for the following variables:

```{r results='asis', echo=FALSE, warning=FALSE}
options(digits=9)
kable(
	summaryTable(.dat$data, var.def= read.csv("../config/variableDefinitions.csv", stringsAsFactors=FALSE)),
	 "markdown", align="l", padding=10)
```

## Locations sampled

Data were sampled at the following locations:

```{r echo=FALSE, fig.width=12, fig.height=10, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, .study)
drawWorldPlot (prepdata)
```

@@

```{r echo=FALSE, fig.width=12, fig.height=10, message=FALSE, warning=FALSE}
repMissingInfo(prepdata)
drawCountryPlot(prepdata)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results='asis'}
kable(locLevelInfo(.dat$data),"markdown", align="l", padding=2)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
kable(standLevelInfo(.dat$data),"markdown", align="l", padding=2)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results="asis"}
kable(spLevelInfo(.dat$data), "markdown", align="l", padding=2)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
metaTable  <-  getMeta(.study)
writeLines(paste0("**",metaTable[,1],"**", ": ", metaTable[,2], "\n"))
```

@@

This is how the study `r .study` fits in the entire dataset (grey). each colour represents a species. A legend of species names with colours is included at the end for reports with 1 < n < 20 species.

```{r fig.height=12, fig.width=12, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata, .dat)
```

>>>>

```{r, echo=FALSE, results="hide"}
study_name <- data_study$key
```

# Report for study: `r study_name`

@@

**Data contributor:** `r data_study$contacts$name`

**Email:** `r paste0(data_study$contacts$email[data_study$contacts$email!=""], collapse = ", ")`

@@

`r paste0("- ", data_study$contacts$address, collapse = "\n")`

@@

**Citation:** `r data_study$references$citation`

**DOI:** `r md_link_doi(bib_element(data_study$bibtex, "doi"))`

**Abstract:** `r  bib_element(data_study$bibtex, "abstract")`

@@

The dataset includes records for `r nrow(data_study$data)` individuals from `r length(unique(data_study$data$species))` species belonging to `r length(unique(data_study$data$family))` family(ies), presenting `r length(unique(data_study$data$pft))` functional type(s), growing in `r length(unique(data_study$data$growingCondition))` condition(s) within `r length(unique(data_study$data$vegetation))` major type(s) of habitat, with data included for the following variables:

```{r summary_table, results='asis', echo=FALSE}
# From the ms functions:
tab <- summary_table(data_study$data, baad$dictionary)
kable(tab[names(tab) != "Studies"], "markdown", align="l", padding=10)
```

```{r world_map, echo=FALSE, fig.width=12, fig.height=10}
map_info <- prep_map_info(data_study$data, study_name)
drawWorldPlot(map_info)
```

@@

```{r country_map, echo=FALSE, fig.width=12, fig.height=10}
report_missing_info(map_info)
drawCountryPlot(map_info)
```

@@

```{r location_level_info, echo=FALSE, comment='', results='asis'}
kable(location_level_info(data_study$data), "markdown", align="l", padding=2)
```

@@

```{r stand_level_info, echo=FALSE, comment='', results="asis"}
kable(stand_level_info(data_study$data), "markdown", align="l", padding=2)
```

@@

```{r species_level_info, echo=FALSE, comment='', results="asis"}
kable(species_level_info(data_study$data), "markdown", align="l", padding=2)
```

@@

```{r metadata, echo=FALSE, comment='', results="asis"}
metadata <- data_study$metadata
writeLines(sprintf("**%s**: %s\n", metadata$Topic, metadata$Description))
```

@@

This is how the study `r study_name` fits in the entire dataset (grey). each colour represents a species. A legend of species names with colours is included at the end for reports with 1 < n < 20 species.

```{r variable_plots, fig.height=12, fig.width=12, echo=FALSE}
report_variable_plots(data_study, baad)
```
